\documentclass[36pt]{article}
\usepackage[a3paper, margin=2in]{geometry}
\usepackage{amsmath}
\author{Wong Ding Feng \and Derrick Chua}
\title{PYP.AI}
\begin{document}
\maketitle
\section{Level of Achievement}
Gemini
\section{Project Scope}
A portal for crowdsourced Past Year Paper solutions
\section{Problem Motivation}
We realised the lack of past year paper solutions for some courses in NUS\@. When we come up with some solutions for past year papers, it would be nice to be able to check against other people's solutions.
\section{Detailed description}
\subsection{Method to sieve out correct answer}
We need real data to know how each method would work out, currently still experimenting. These are a few that we had come up with.
\subsubsection{Reddit style of upvote}
Upvotes pull it up.Add some time based weight to pull it down. This is to allow for possibly newer better answers.
\subsubsection{Similarity comparison through NLTK}
Great minds think alike, thats the idea behind this.
Using python NLTK or other machine learning methods, possibly doing word count to find similarity in sentences. Then this could possibly be a correct answer.
\subsection{Rebuttal methods}
There are some questions that trick the majority into getting the wrong answer, to allow for the few to submit meaningful corrections to the majority's answer. 
\subsection{Tagging and Indexing}
Information is useful becaused it is indexed, try to create some auto indexing algorithms.
\section{Technologies and tools}
\begin{itemize}
    \item Backend
    \begin{itemize}
        \item Node.js
            \begin{itemize}
                \item Passport.js
            \end{itemize}
        \item Express
        \item NLTK
     \end{itemize}
\item Frontend
    \begin{itemize}
        \item React
    \end{itemize}
\end{itemize}

\section{Development Plan}
\begin{tabular}[pos]{| l | l |}
    \hline
    Parse past year papers using OCR (otherwise manual) & June week 1 \\
    \hline
    Create forum & June week 2  \\
    \hline
    Sieve our answer & June week 3 \& 4 \\
    \hline
    Crypto-currency & July \\
    \hline
\end{tabular}

\end{document}
